% در این فایل، عنوان پایان‌نامه، مشخصات خود و چکیده پایان‌نامه را به انگلیسی وارد کنید.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{latin}
\latindepartment{Computer}
\latintitle{Realtime Face Recognition in Unconstraint Environments}
\firstlatinsupervisor{DR. Hamid Reza Pour Reza}
%\secondlatinsupervisor{Second Supervisor}
firstlatinadvisor{DR. Boshra Rajaee}
%\secondlatinadvisor{Second Advisor}
\latinname{Sajjad}
\latinsurname{Aemmi}
\latinthesisdate{June 2021}

\enabstract{
\subsection*{Abstract}
\thispagestyle{empty}
In recent years, due to the use of deep learning, face recognition technology has witnessed significant advances. However, data-driven strategies present a challenge: Images sent to the face recognition system are not always suitable for detection, and may include low-resolution faces, blurry moving faces, blocked faces, and even back problems. There are grounds. Unfortunately, since the face recognition engine has never seen such low-quality faces before, it is likely to make the wrong decisions about them. This dissertation focuses on the immediate recognition of faces in uncontrolled environments, which consists of two main parts: face finding and face recognition. The proposed method is in the face recognition section. The ultimate goal of designing the software part of a smart glasses is for the blind. When a blind person uses glasses and walks in public, the camera mounted on the glasses examines the faces of people in the viewing angle, and if a familiar face is found, the person is identified. And his name is read aloud to the blind man. 

In implementing this system, which should be used in public places, sidewalks and uncontrolled environments, there are several important challenges such as uneven lighting, obstruction, out-of-focus blur, and unfavorable angle of the face to the camera. On the other hand, this system must behave immediately. Because there is not much opportunity to identify a person walking down the street next to the camera. On the other hand, due to the execution of processes on the mobile processor, resource constraints must also be considered and the algorithm used must have the least complexity of time and memory. For this purpose, we based our research on the MobileNetV3 architecture. In this dissertation, the main focus of studies is on designing an efficient and suitable algorithm for the instantaneous face recognition step in unrestricted conditions. In addition to the above, we assume that we have limited data from each category. To meet this challenge, we use one shot learning and few shot learning methods. By examining the results of this study on LFW and YouTube Faces datasets, the accuracy of our proposed method was 96\% and 94\%, respectively, which is higher accuracy than similar methods.


Keywords: Face Identification، Deep Learning، Image Processing، Real-Time، Classification
}
\latinyazdtitle
\end{latin}
